### 2021-03-05 text/draft.tex
metrics general

\begin{figure}
\centering
\includegraphics{images/metrics_f1_top20.pdf}
\caption{Top 20 Annif configurations by F1-score.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/metrics_all_project+abstract.pdf}
\caption{Distribution of weighted F1-scores per class of algorithm
(left) and per class of text basis (right).}
\end{figure}

>>>>

In this section I will discuss the general results of assessing the
performance of the 100 Annif configurations versus the native gold
standard with respect to the Edoc sample data set.

Let us first consider overall performance. Here the most remarkable
result is that Wikidata configurations outperformed YSO configurations
(see Figure X). However, the explanation of this effect is not evident.
The two main explanatory hypotheses are 1. that the suggestions by the
Wikidata configurations are more salient, or 2. that the native gold
standard is biased towards Wikidata due to its higher coverage of QIDs
as compared to YSO IDs. By contrast, the Wikidata configurations are
more productive than the YSO configurations, and the reason for this
effect is the higher coverage of QIDs as compared to YSO IDs (see Figure
Y). By ``productivity'' I mean that the absolute number of assigned
subject terms. So Wikidata configurations are not only qualitatively but
also quantitatively superior to YSO configurations.

\begin{figure}
\centering
\includegraphics{images/metrics_all_project+abstract.pdf}
\caption{Distribution of weighted F1-scores per class of algorithm
(left) and per class of text basis (right). Figure X.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/metrics_all_productivity.pdf}
\caption{The distribution of cumulative sample size per class of Annif
configuration. Figure Y}
\end{figure}

Furthermore, the four YSO configurations are more or less on par: the
\texttt{yso-bonsai-en}, \texttt{yso-en}, and \texttt{yso-fasttext-en}
configurations perform very similarily and are slightly outperformed by
\texttt{yso-maui-en}.

\begin{figure}
\centering
\includegraphics{images/metrics_f1_top20.pdf}
\caption{The top 20 Annif configurations by F1-score.}
\end{figure}

@@
